

\section{Killing bacteria}

From a human perspective, there are many situations where it is desired to kill or inhibit bacterial growth.
%
That makes it very relevant to learn about bacterial survival mechanisms.
%
Targeting the components of these survival mechanisms specifically might 
decrease bacterial proliferation in settings where this is not desired.
%
As explained in chapter \ref{chapter:filarecovery},
filamentation, pausing bacterial division in response to 
%



\section{Division laws in filamentous bacteria}

In chapter \ref{chapter:filarecovery}, we described how bacteria manage resuming their divisions after they 
paused the division process due to situations they experienced as stressful.
%
There are many situations that can induce filamentation,
which is thought to be a response that helps bacteria survive.
%
From a human perspective, there are many situations where it is desired to kill or inhibit bacterial growth.
Examples are clinical settings and food preservation.
%
Thus, from that perspective, it is very relevant to learn about bacterial survival mechanisms.
%
Targeting the components of these survival mechanisms specifically might 
decrease bacterial proliferation in settings where this is not desired.



\section{lala}



As described in chapter \ref{chapter:filarecovery}, bacteria are often confronted with adverse situations.
%


Such situations include for example cold -- perhaps during food storage -- and antibiotic treatment in case of pathogenic bacteria.
%
These 