



% REMEMBER I WAS EDITING ACKNOWLEDGEMENTS_TEMP































\chapter*{Acknowledgements}
\addcontentsline{toc}{chapter}{Acknowledgements}

Not only the nature of the work, but also the environment in which you work is important for your motivation and happiness.
%
I'm glad to have done my PhD at AMOLF, which provided 
a lively social scene and
is populated by friendly and helpful people.



First and foremost I'd like to thank Sander here, 
for providing me the opportunity to work on the fascinating topics described in this thesis and being my mentor the past years.
%as he 
%provided me the opportunity to work on the fascinating topics that I have worked on for the past years.
%
In our many discussions,
perhaps after a slightly convoluted argument from me,  
you have often and repeatedly asked "but what is the key question?".
%
I have more and more come to appreciate the wisdom of asking this question, 
and the importance of answering it.
Why are we doing what we are doing and what is the use of it?
Being able to precisely and concisely formulate the answer to this question, 
is a key quality to practice science well. 
%
You have also taught me to carefully look at data,
and ask what answers are in there --- 
answers that not necessarily answer our original question,
but perhaps another, more interesting one. 
%
Cynics might call this quality salesmanship,
but I think that undervalues the importance
of being able to assess the value of features that we observe in our scientific data and place it in a larger context.

% PROFESSIONAL "FRIENDS" FROM GROUP

I am also glad to have worked with so many great people.
%
My (former) colleagues from the lab who worked on the same topic: 
Noreen, Dmitry, Ferhat, Katja, Sebastian and Rutger R..
%
Noreen, thank you for your rigorous explanations of how to do experiments,
and for being an example of how to work neatly and accurately.
%
Dmitry, thank you for showing me how to operate microfluidic devices,
I especially enjoyed (and learned from) our macGyver sessions trying to improve the device, 
I also greatly enjoyed our political discussions.
%
Ferhat, without you the device that I mundanely refer to as the "microfluidic device 2" would never have been a success,
I really appreciate our collaboration, and your "let's do it" mentality. Glorious.
%
Katja, I deeply appreciate your sharp mind and insightful observations; I am grateful for 
our discussions (often at the coffee corner) where you often had great advice on professional/scientific matters. 
%
Sebastian, thank you for your insightful input,
and for being an example of how it sometimes works very well to be headstrong. 
%
Rutger, I thank your for your patience in explaining me experimental protocols; 
also, I have learned from your people skills.

% STUDENTS

A special thanks goes out to the two students I had the privilege to supervise, Nick and Giulia.
%
I hope you have learned from me.
I have learned a tremendous deal from supervising you.
%
It was very insightful to see projects through the eyes of a supervisor. 
I also like to think that I have grown as a teacher, 
because I had to think about the best way to convince you that 
approach X or Y was the best.
%
Nick, I greatly admire your work ethics and skill in the lab, 
and greatly appreciate your positive attitude.
%
Giulia, I really enjoyed our discussions,
both on science and life in general,
you have a very sharp mind.


% COLLABORATORS

> Laurens Krah
> Benjamin Towbin
> Petra
> Rutger Hermsen
\red{+andrew?}







%Sander
%> To search for the key question
%> To look for the interesting story



\section*{Names}

Don't forget:



Remember to thank:
> At (Ton) de Waart
> Giulia Bergamaschi
> Nick de Lange
> Andrew Mugler [attitude towards science]
> Brian Munsky


> Laurens Krah
> Benjamin Towbin
> Petra
> Rutger Hermsen

Sander

AMOLF

Ferhat
Vanda
katja taute
sebastian gude
Mario
Eline
(Roeland, Moshin, )
david 
Rebecca
Xuan 
Anne-Bart
Florian
(check lab page)

Joris
Johannes
Mark
Rik
Robin
Esther
Roland Dries

(Joris)
Noreen
Stephen
Adithya
Thomas Ouldride/Addenbrook *anecdote my system of names?* + Christina
Agata

Floortje
Niels
Tom
Clyde

Nicola
simone kienle
yuval
bart vos
christina
magdalena
jeanette
Matthijs
Harmen
Viktoria
Michele
Jacopo
Giulia Malaguti
Anders
Fatemeh



Pieter Rein
Bela
Tom



simone boskamp
yvonne


Hinco
Marko


Parents
Sonja

















